---
title: "MOM vs MLE Beta phi recovery at production sample sizes"
subtitle: "Bootstrap validation across the Brysbaert et al. (2024) corpus"
author: "Ian Hussey"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    code_folding: hide
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE,
                      cache = TRUE, fig.width = 11, fig.height = 7)
```

```{r deps}
suppressPackageStartupMessages({
  library(tidyverse)
  library(betareg)
  library(knitr)
})
source("extract_brysbaert_functions.R")
```

# Why this analysis exists

The full-N MOM vs MLE comparison done elsewhere mostly answers "does the
constant-phi Beta model fit this scale?" — at N in the thousands, both
estimators are essentially asymptotic and recover the same population
phi. That tells us nothing useful about the production case, where
someone has reported `(M, SD)` from `n = 80` and we want to derive
plausibility bounds from that single summary.

To validate MOM for production use we need to ask:

> At realistic clinical-trial sample sizes, how close is the MOM phi
> derived from `(M, SD)` to the MLE phi we'd get from the same
> participants' raw items?

This Rmd bootstraps subsamples of multiple sizes from each well-behaved
Brysbaert dataset, computes both MOM and MLE phi per subsample, and
reports their bias and variance against the full-N MLE as ground truth.

# Selecting datasets

Restrictions:

- `n_kept >= 500` so we can bootstrap up to `N = 500`
- catalog `min/max` agrees with observed (not in `range_check`) — we
  want clean data, not fights with mis-specified ranges
- mean POMP between 0.15 and 0.85 — extreme-mean scales are known
  Beta-misfit cases (boundary mass) and would conflate "Beta is wrong"
  with "MOM is biased at small N"

```{r select-datasets}
in_rc <- dplyr::transmute(range_check, scale, source, in_range_check = TRUE)

candidates <- brysbaert_load_log |>
  dplyr::filter(ok, n_kept >= 500) |>
  dplyr::left_join(in_rc, by = c("scale", "source")) |>
  dplyr::filter(is.na(in_range_check)) |>
  dplyr::select(scale_folder, data_file, scale, source, n_kept)

# Mean POMP per dataset (computed cheaply from sumscores)
mean_pomp_per_dataset <- dat_brysbaert_sumscores |>
  dplyr::group_by(scale, source) |>
  dplyr::summarise(
    mean_pomp = mean((sumscore / n_items - min_response) /
                     (max_response - min_response), na.rm = TRUE),
    .groups = "drop"
  )

candidates <- candidates |>
  dplyr::left_join(mean_pomp_per_dataset, by = c("scale", "source")) |>
  dplyr::filter(mean_pomp >= 0.15, mean_pomp <= 0.85)

cat("Candidate datasets after filtering:", nrow(candidates), "\n")
candidates |>
  dplyr::select(scale, source, n_kept, mean_pomp) |>
  dplyr::arrange(desc(n_kept)) |>
  kable(digits = 3, caption = "Datasets entering the bootstrap")
```

# Build participant POMP vectors

```{r build-pomp, cache=TRUE}
candidates$pomp <- lapply(seq_len(nrow(candidates)), function(i) {
  tryCatch({
    d <- get_dataset_items(candidates$scale_folder[i], candidates$data_file[i])
    participant_pomp(d)
  }, error = function(e) NULL)
})

candidates$n_pomp <- sapply(candidates$pomp,
                            function(x) if (is.null(x)) 0L else length(x))
candidates <- candidates[candidates$n_pomp >= 500, ]
cat("Datasets with >=500 valid POMP scores:", nrow(candidates), "\n")
```

# Bootstrap

`B = 200` reps per (scale, N). Sample sizes span typical psychology
sample sizes: 30 (very small RCT arm), 50, 100 (median trial arm), 200,
500. Larger N would already be near-asymptotic.

```{r bootstrap, cache=TRUE}
N_GRID <- c(30, 50, 100, 200, 500)
B      <- 200

boot_results <- purrr::map_dfr(seq_len(nrow(candidates)), function(i) {
  bootstrap_phi_finite_sample(
    pomp_full = candidates$pomp[[i]],
    scale     = candidates$scale[i],
    source    = candidates$source[i],
    N_grid    = N_GRID,
    B         = B,
    seed      = i
  )
})

# Persist for downstream use
if (!dir.exists("processed")) dir.create("processed")
saveRDS(boot_results, "processed/mom_mle_bootstrap.rds")
cat("Bootstrap rows:", nrow(boot_results), "\n")
```

# Headline: corpus-level MOM vs MLE agreement at each N

This is the main result. Across all candidate datasets, in each
subsample of size N: how close is MOM phi to MLE phi (in the same
subsample)? And how close is each to the full-N MLE ground truth?

```{r headline}
headline <- boot_results |>
  dplyr::filter(is.finite(phi_mom), is.finite(phi_mle),
                is.finite(phi_star), phi_star > 0) |>
  dplyr::group_by(N) |>
  dplyr::summarise(
    n_subsamples       = dplyr::n(),
    median_rel_bias_mom = round(median((phi_mom - phi_star) / phi_star), 3),
    median_rel_bias_mle = round(median((phi_mle - phi_star) / phi_star), 3),
    median_abs_diff_mom_mle = round(median(abs(phi_mom - phi_mle) / phi_mle), 3),
    q90_abs_diff_mom_mle    = round(quantile(abs(phi_mom - phi_mle) / phi_mle, 0.9), 3),
    .groups = "drop"
  )

kable(headline,
      caption = paste("Corpus-wide MOM vs MLE recovery at finite N. Columns:",
                      "median relative bias against full-N MLE truth (positive =",
                      "estimator overshoots truth) and median / 90th-percentile",
                      "absolute relative difference between MOM and MLE in the",
                      "same subsample."))
```

# Per-dataset summary

```{r per-dataset-summary}
boot_summary <- boot_results |>
  dplyr::filter(is.finite(phi_mom), is.finite(phi_mle),
                is.finite(phi_star), phi_star > 0) |>
  dplyr::group_by(scale, source, N) |>
  dplyr::summarise(
    phi_star    = unique(phi_star)[1],
    phi_mom_med = median(phi_mom, na.rm = TRUE),
    phi_mle_med = median(phi_mle, na.rm = TRUE),
    phi_mom_q25 = quantile(phi_mom, 0.25, na.rm = TRUE),
    phi_mom_q75 = quantile(phi_mom, 0.75, na.rm = TRUE),
    phi_mle_q25 = quantile(phi_mle, 0.25, na.rm = TRUE),
    phi_mle_q75 = quantile(phi_mle, 0.75, na.rm = TRUE),
    .groups = "drop"
  )
```

# Plot: phi recovery vs N, faceted by dataset

Each facet is one Brysbaert dataset. Y-axis is `phi_estimator / phi_star`.
Dashed line at 1 = perfect recovery. Ribbons are IQR across `B`
bootstrap subsamples.

```{r plot-recovery, fig.height=11}
plot_df <- boot_summary |>
  dplyr::mutate(
    mom_ratio = phi_mom_med / phi_star,
    mle_ratio = phi_mle_med / phi_star,
    mom_lo    = phi_mom_q25 / phi_star,
    mom_hi    = phi_mom_q75 / phi_star,
    mle_lo    = phi_mle_q25 / phi_star,
    mle_hi    = phi_mle_q75 / phi_star,
    facet_lab = sprintf("%s\n%s (phi*=%.1f)", scale, source, phi_star)
  )

ggplot(plot_df, aes(x = N)) +
  geom_hline(yintercept = 1, linetype = "dashed", colour = "grey60") +
  geom_ribbon(aes(ymin = mom_lo, ymax = mom_hi),
              fill = "#1a5fb4", alpha = 0.18) +
  geom_ribbon(aes(ymin = mle_lo, ymax = mle_hi),
              fill = "#c64600", alpha = 0.18) +
  geom_line(aes(y = mom_ratio, colour = "MOM"), linewidth = 0.9) +
  geom_line(aes(y = mle_ratio, colour = "MLE"), linewidth = 0.9) +
  geom_point(aes(y = mom_ratio, colour = "MOM"), size = 1.3) +
  geom_point(aes(y = mle_ratio, colour = "MLE"), size = 1.3) +
  scale_x_log10(breaks = N_GRID) +
  scale_colour_manual(values = c("MOM" = "#1a5fb4", "MLE" = "#c64600")) +
  facet_wrap(~ facet_lab, scales = "free_y", ncol = 4) +
  labs(x = "Subsample size N (log scale)",
       y = "Estimated phi / full-N MLE phi*",
       colour = NULL,
       caption = "Ribbons = IQR across bootstrap reps. Dashed = perfect recovery.") +
  theme_linedraw(base_size = 10) +
  theme(legend.position = "bottom",
        strip.text = element_text(size = 8))
```

# Same-subsample MOM vs MLE agreement

The most production-relevant question: in the SAME subsample, how close
are MOM and MLE? This is what the meta-analytic plausibility check
gambles on.

```{r same-sample-agreement}
agreement <- boot_results |>
  dplyr::filter(is.finite(phi_mom), is.finite(phi_mle), phi_mle > 0) |>
  dplyr::mutate(rel_diff = (phi_mom - phi_mle) / phi_mle) |>
  dplyr::group_by(N) |>
  dplyr::summarise(
    n          = dplyr::n(),
    median     = round(median(rel_diff), 3),
    p10        = round(quantile(rel_diff, 0.10), 3),
    p90        = round(quantile(rel_diff, 0.90), 3),
    abs_med    = round(median(abs(rel_diff)), 3),
    abs_p90    = round(quantile(abs(rel_diff), 0.90), 3),
    pct_within_10pct = round(mean(abs(rel_diff) < 0.10), 3),
    pct_within_25pct = round(mean(abs(rel_diff) < 0.25), 3),
    .groups = "drop"
  )

kable(agreement,
      caption = "(phi_MOM - phi_MLE) / phi_MLE in matched subsamples")
```

```{r plot-agreement, fig.height=4}
boot_results |>
  dplyr::filter(is.finite(phi_mom), is.finite(phi_mle), phi_mle > 0) |>
  dplyr::mutate(rel_diff = (phi_mom - phi_mle) / phi_mle,
                N = factor(N, levels = N_GRID)) |>
  ggplot(aes(N, rel_diff)) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey50") +
  geom_violin(fill = "#1a5fb4", alpha = 0.2, colour = "#1a5fb4") +
  geom_boxplot(width = 0.15, outlier.size = 0.4, fill = "white") +
  coord_cartesian(ylim = c(-1, 1)) +
  labs(x = "Subsample size N", y = "(phi_MOM - phi_MLE) / phi_MLE",
       caption = "Distribution across all (scale x bootstrap) reps. Clipped to +/-100% for readability.") +
  theme_linedraw(base_size = 12)
```

# Interpretation

Read this section after running the chunks above. The headline table
and the same-subsample agreement plot answer the production question
directly:

- If `pct_within_25pct` at `N = 80–100` is high (say >0.8), MOM is
  defensible for plausibility-bound use on typical clinical-trial
  summary stats.
- If `median_rel_bias_mom` is appreciably non-zero at small N, MOM
  systematically over- or under-estimates phi, which translates into
  systematic SMD-bound bias.
- If `q90_abs_diff_mom_mle` is large (say >0.5), the MOM bound from a
  single (M, SD) report can be substantially off — useful caveat for
  any production tool.

Compare the headline numbers at different N values to see how fast the
MOM/MLE gap shrinks. The figure shows whether some scales misbehave
more than others — that signals scale-specific Beta-fit weakness rather
than a generic MOM problem.
