---
title: "Simulation of maximum plausible SMD given scale range-to-SD ratio"
author: "Ian Hussey" 
date: "`r format(Sys.time(), '%d %B, %Y')`"
always_allow_html: true
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float:
      collapsed: false
      fontsize: 10pt
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE, 
                      message = FALSE, 
                      warning = FALSE)

# disable scientific notation
options(scipen = 999) 

```

# Motivation and logic

## The problem

When evaluating the plausibility of reported effect sizes in psychology — whether for forensic purposes, meta-analytic quality control, or power analysis — it is useful to know the *maximum* standardized mean difference (SMD, Cohen's *d*) that could plausibly be observed on a given self-report scale. A reported *d* that exceeds this ceiling should raise red flags, because it implies a mean difference that the scale cannot physically accommodate.

```{r}

library(tidyverse)

mu_control <- 32
sigma_control <- 9
target_var <- sigma_control^2 
n_per_group <- 1000

# Calculate dispersion (size) for each group to keep SD constant at 8
theta_control <- round(mu_control^2 / (target_var - mu_control), 1)

plot_data <- tibble(x = 0:63) %>%
  mutate(
    Probability = dnbinom(x, mu = mu_control, size = theta_control)
  )

ggplot(plot_data, aes(x = x, y = Probability)) +
  geom_area(alpha = 0.6, position = "identity", fill = "steelblue") +
  # Vertical Lines
  geom_vline(xintercept = mu_control - sigma_control*0, linetype = "dashed", color = "grey0") +
  geom_vline(xintercept = mu_control - sigma_control*1, linetype = "dotted", color = "grey0") +
  geom_vline(xintercept = mu_control - sigma_control*2, linetype = "dotted", color = "grey0") +
  geom_vline(xintercept = mu_control - sigma_control*3, linetype = "dotted", color = "grey0") +
  # Annotations
  annotate("text", x = mu_control - sigma_control*0, y = 0, angle = 90, label = "Mean at baseline", vjust = 2, hjust = -.05) +
  annotate("text", x = mu_control - sigma_control*1, y = 0, angle = 90, label = "Mean at post if Cohen's d = -1", vjust = 2, hjust = -.02) +
  annotate("text", x = mu_control - sigma_control*2, y = 0, angle = 90, label = "Mean at post if Cohen's d = -2", vjust = 2, hjust = -.02) +
  annotate("text", x = mu_control - sigma_control*3, y = 0, angle = 90, label = "Mean at post if Cohen's d = -3", vjust = 2, hjust = -.02) +
  scale_y_continuous(breaks = scales::breaks_pretty(n = 5)) +
  scale_x_continuous(
    name = "Depression (BDI-II)",
    breaks = scales::breaks_pretty(n = 9),
    limits = c(0, 63)
  ) +
  theme_classic() +
  labs(title = "Simulated population: treatment-seeking depression",
       subtitle = "Negative binomial distribution with M = 32, SD = 9")


```


```{r}

# Parameters
mu_control    <- 32
sigma_control <- 9
target_var    <- sigma_control^2
ds            <- c(0, 1, 2, 3) # Cohen's d values to simulate

# Generate distributions
plot_data <- ds %>%
  map_df(~{
    current_mu <- mu_control - (.x * sigma_control)
    # Calculate theta (size) to keep variance constant
    # Formula: size = mu^2 / (var - mu)
    current_theta <- current_mu^2 / (target_var - current_mu)
    
    tibble(
      x = 0:63,
      d = as.factor(.x),
      mu = current_mu,
      probability = dnbinom(x, mu = current_mu, size = current_theta)
    )
  })

# Plotting
ggplot(plot_data, aes(x = x, y = probability, fill = fct_rev(d))) +
  geom_area(alpha = 0.8, position = "identity", color = "white", size = 0.3) +
  # Vertical lines for group means
  geom_vline(aes(xintercept = mu, color = fct_rev(d)), 
             linetype = "dashed", alpha = 0.8, show.legend = FALSE) +
  #scale_fill_brewer(palette = "Blues", name = "Cohen's d") +
  #scale_color_brewer(palette = "Blues") +
  scale_color_viridis_d(begin = 0.3, end = 0.7) +
  scale_fill_viridis_d(begin = 0.3, end = 0.7, name = "Cohen's d") +
  scale_x_continuous(breaks = seq(0, 63, 5), limits = c(0, 63)) +
  labs(
    title = "BDI-II Distribution Shifts by Effect Size",
    subtitle = "Constant Variance (SD=9), Mean Control = 32 (Severe)",
    x = "BDI-II Score",
    y = "Density"
  ) +
  theme_minimal() +
  theme(panel.grid.minor = element_blank())

```

## Why scale range constrains SMDs

A self-report scale has a fixed range (max − min). The standardized mean difference *d* = (M~treatment~ − M~control~) / SD~pooled~ is bounded because the numerator — the raw mean difference — cannot exceed the scale range. A naive upper bound is therefore Range / SD, the ratio of the scale's scoring range to its standard deviation. However, several factors make the *achievable* maximum considerably smaller than this naive bound:

1. **The control mean is not at the boundary.** For symptom scales (e.g., BDI-II, PHQ-9), untreated clinical groups average around 30–50% of the scale range, not at the ceiling. For community samples, the control mean sits near the floor. Either way, the control mean "uses up" a portion of the range before any treatment effect is applied.

2. **The treatment mean cannot reach the opposite boundary.** Even a maximally effective intervention leaves some residual variance — not every participant reaches the floor (or ceiling). The treatment group mean must therefore sit at least ~1 SD from the boundary.

3. **Variance compression near boundaries.** As a group mean approaches a scale boundary, its variance is squeezed by floor/ceiling effects. This *deflates* the pooled SD, which paradoxically could *inflate* the SMD ratio, but at extreme compression the SMD becomes uninterpretable. We model this compression explicitly.

4. **Sampling noise at small N.** Small studies have imprecise estimates of both means and SDs. By chance, a small study can observe a *d* considerably larger than the true population value. This means the plausible *observed* ceiling depends on sample size: smaller studies can produce more extreme values through noise alone.

## The simulation approach

For each combination of scale archetype, effect size level, and sample size, we:

1. Generate bounded data for both groups using beta distributions parameterized to match the target mean and SD within the scale bounds.
2. Compute Cohen's *d* with pooled SD.
3. Repeat many times to build a sampling distribution of observed *d*.
4. Extract the mean, 95th percentile, and 99th percentile of this distribution.

The 95th percentile is the key diagnostic quantity: it represents the largest *d* that a study could plausibly report, accounting for both the true maximum effect the scale can accommodate and the additional inflation from sampling noise.

## Why scale type matters

The maximum achievable SMD depends critically on where the control group mean sits relative to the scale boundaries, which varies systematically by scale type:

- **Symptom scales in clinical samples** (e.g., BDI-II in depressed outpatients): The control mean sits moderately high (~35–50% of range), leaving substantial room for treatment to reduce scores. Maximum true *d* ≈ 3.0.
- **Symptom scales in community samples** (e.g., PHQ-9 in general population): The control mean sits near the floor (~10–15% of range), because most healthy people score near zero. There is almost no room for further reduction. Maximum true *d* ≈ 1.0–1.3. This is the most constrained scenario.
- **Well-being scales** (e.g., SWLS, RSES): The control mean typically sits near the middle of the range (~45–55%), with treatment pushing scores upward. Maximum true *d* ≈ 2.9–4.5.
- **Trait measures** (e.g., STAI-Trait, NEO-FFI Neuroticism): The control mean often sits well away from both boundaries, and trait measures tend to be more normally distributed. This gives the most room for separation. Maximum true *d* ≈ 3.1–5.2.

## Scale archetypes and sources for mean and SD estimates

The simulation uses 12 scale archetypes based on widely-used self-report measures. The control group means and SDs are drawn from published normative data and large validation studies:

| Scale | Items | Scoring | Range | Control mean | Control SD | Source |
|-------|-------|---------|-------|-------------|-----------|--------|
| BDI-II (clinical) | 21 | 0–3 | 0–63 | 25 | 10.0 | Beck, Steer & Brown (1996) manual: outpatient M ≈ 22.5, SD ≈ 12.8; rounded for moderate severity |
| PHQ-9 (clinical) | 9 | 0–3 | 0–27 | 14 | 5.5 | Cameron et al. (2008) primary care referrals: SD ≈ 6.5; M = 14 approximates moderate depression |
| PHQ-9 (community) | 9 | 0–3 | 0–27 | 3 | 3.6 | Kocalevent, Hinz & Brähler (2013) German general population N = 5,018: M ≈ 2.9, SD ≈ 3.6 |
| BDI-II (community) | 21 | 0–3 | 0–63 | 8 | 8.5 | Whisman & Richardson (2015) US college students N = 15,233: SD ≈ 8.5; community means typically 6–10 |
| CES-D (clinical) | 20 | 0–3 | 0–60 | 24 | 10.0 | Radloff (1977): psychiatric sample M ≈ 24, community SD ≈ 8.5, clinical SD somewhat larger |
| CES-D (community) | 20 | 0–3 | 0–60 | 9 | 8.2 | Radloff (1977) community samples: M ≈ 8.6–9.3, SD ≈ 7.9–8.6 |
| SWLS | 5 | 1–7 | 5–35 | 20 | 6.2 | Diener et al. (1985), Pavot & Diener (1993): M ≈ 23–26 (students), SD ≈ 6.4; M = 20 as conservative community estimate |
| RSES (0–30) | 10 | 0–3 | 0–30 | 16 | 5.3 | Sinclair et al. (2010) US adults N = 503: M ≈ 22.6, SD ≈ 5.8; M = 16 reflects lower-functioning control |
| PANAS-PA | 10 | 1–5 | 10–50 | 32 | 7.0 | Watson et al. (1988) "general" instruction: M ≈ 35, SD ≈ 6.4; Crawford & Henry (2004): SD ≈ 7.7 |
| STAI-Trait | 20 | 1–4 | 20–80 | 38 | 9.8 | Spielberger (1983) manual: working adults SD ≈ 9.9–10.0, college students similar |
| PSS-10 | 10 | 0–4 | 0–40 | 17 | 6.2 | Cohen & Williamson (1988) US probability sample N = 2,387: M ≈ 13, SD ≈ 6.4; Klein et al. (2016): SD ≈ 5.9 |
| NEO-FFI Neuroticism | 12 | 0–4 | 0–48 | 19 | 7.7 | Costa & McCrae (1992) manual: M ≈ 19.1, SD ≈ 7.7 |

## Modelling variance compression

As a treatment group mean approaches a scale boundary, the distribution gets "squeezed" — there is less room for scores to spread out, reducing the SD. We model this using a square-root proportional compression: the treatment SD shrinks as √(distance to boundary / control distance to boundary). This is a conservative approximation: it ensures that a treatment group whose mean is at 25% of the available distance from the boundary retains 50% of the original SD, which is broadly consistent with the behavior of beta distributions near their bounds.

# Dependencies and setup

```{r}

library(tidyverse)
library(furrr)
library(scales)

plan(multisession, workers = availableCores() - 1)
set.seed(42)

# shared plot theme
theme_set(
  theme_minimal(base_size = 12) +
    theme(
      panel.grid.minor = element_blank(),
      plot.title       = element_text(face = "bold", size = 13),
      plot.subtitle    = element_text(colour = "grey40", size = 10),
      strip.text       = element_text(face = "bold"),
      legend.position  = "right"
    )
)

scale_type_colours <- c(
  "symptom_clinical"  = "#d62728",
  "symptom_community" = "#ff7f0e",
  "trait"             = "#1f77b4",
  "wellbeing"         = "#2ca02c"
)

scale_type_labels <- c(
  "symptom_clinical"  = "Symptom (clinical)",
  "symptom_community" = "Symptom (community)",
  "trait"             = "Trait",
  "wellbeing"         = "Well-being"
)

```

# Functions

```{r}

#' Generate bounded random data using a beta distribution
#'
#' Produces a sample of n values on the interval [scale_min, scale_max]
#' whose expected mean and SD match the specified targets. This is achieved
#' by reparameterizing the beta distribution in terms of mean and variance
#' on the unit interval, then rescaling to the desired range.
#'
#' The beta distribution is used because it naturally produces data on a
#' bounded interval and can be parameterized to match a wide range of
#' distributional shapes (symmetric, left-skewed, right-skewed) depending
#' on the target mean and SD.
#'
#' Returns NULL if the target mean/SD combination is not achievable within
#' the beta distribution's constraints (i.e., when the variance exceeds
#' mu * (1 - mu) on the unit scale, or when the resulting shape parameters
#' are degenerate). This allows the simulation to gracefully skip
#' impossible parameter combinations.
#'
#' @param n       Integer. Number of observations to generate.
#' @param mean_val Numeric. Target mean on the [scale_min, scale_max] scale.
#' @param sd_val  Numeric. Target SD on the [scale_min, scale_max] scale.
#' @param scale_min Numeric. Lower bound of the scale.
#' @param scale_max Numeric. Upper bound of the scale.
#'
#' @return Numeric vector of length n, or NULL if parameters are degenerate.
rbounded <- function(n, mean_val, sd_val, scale_min, scale_max) {
  rng <- scale_max - scale_min
  mu <- (mean_val - scale_min) / rng
  sigma <- sd_val / rng
  var_ <- sigma^2
  if (var_ >= mu * (1 - mu)) return(NULL)
  phi <- mu * (1 - mu) / var_ - 1
  if (phi <= 0) return(NULL)
  a <- mu * phi; b <- (1 - mu) * phi
  if (a <= 0.01 | b <= 0.01) return(NULL)
  rbeta(n, a, b) * rng + scale_min
}


#' Compute Cohen's d with pooled standard deviation
#'
#' Calculates the standardized mean difference between two independent
#' groups using the pooled SD (square root of the weighted average of
#' the two group variances). This is the standard formulation used in
#' meta-analysis for between-group designs.
#'
#' Returns NA if the pooled SD is effectively zero (< 1e-10), which can
#' occur when data are extremely compressed near a boundary.
#'
#' @param x_treat Numeric vector. Treatment group scores.
#' @param x_ctrl  Numeric vector. Control group scores.
#'
#' @return Numeric scalar: (M_treat - M_ctrl) / SD_pooled.
cohens_d <- function(x_treat, x_ctrl) {
  n1 <- length(x_treat); n2 <- length(x_ctrl)
  sp <- sqrt(((n1 - 1) * var(x_treat) + (n2 - 1) * var(x_ctrl)) / (n1 + n2 - 2))
  if (sp < 1e-10) return(NA_real_)
  (mean(x_treat) - mean(x_ctrl)) / sp
}


#' Simulate a single replication of a two-group comparison
#'
#' Generates one pair of treatment and control group samples using
#' rbounded(), then computes Cohen's d. The direction parameter
#' determines which group is expected to score higher: for symptom
#' scales ("down"), the control group scores higher and d is computed
#' as control minus treatment; for well-being/trait scales ("up"),
#' d is computed as treatment minus control. This ensures d is always
#' positive when the treatment is effective.
#'
#' @param rep_id    Integer. Replication index (unused but included for
#'                  compatibility with map functions).
#' @param n_per     Integer. Sample size per group.
#' @param ctrl_mean Numeric. Control group population mean.
#' @param ctrl_sd   Numeric. Control group population SD.
#' @param treat_mean Numeric. Treatment group population mean.
#' @param treat_sd  Numeric. Treatment group population SD.
#' @param scale_min Numeric. Lower bound of the scale.
#' @param scale_max Numeric. Upper bound of the scale.
#' @param direction Character. "down" if treatment reduces scores
#'                  (symptom scales), "up" if treatment increases
#'                  scores (well-being/trait scales).
#'
#' @return Numeric scalar: observed Cohen's d for this replication,
#'         or NA if data generation failed.
sim_one_rep <- function(rep_id, n_per, ctrl_mean, ctrl_sd, treat_mean, treat_sd,
                        scale_min, scale_max, direction) {
  ctrl_data  <- rbounded(n_per, ctrl_mean, ctrl_sd, scale_min, scale_max)
  treat_data <- rbounded(n_per, treat_mean, treat_sd, scale_min, scale_max)
  if (is.null(ctrl_data) || is.null(treat_data)) return(NA_real_)
  if (direction == "down") cohens_d(ctrl_data, treat_data) else cohens_d(treat_data, ctrl_data)
}


#' Run a full simulation for one parameter condition
#'
#' Performs n_reps replications of the two-group comparison for a
#' single row of the parameter grid. Each replication generates fresh
#' samples and computes Cohen's d. The function then summarizes the
#' resulting sampling distribution by computing the mean, SD, and
#' several quantiles (P05, P95, P99) of the observed d values.
#'
#' The P95 and P99 are the key diagnostic quantities: they represent
#' the largest d values that could be observed at this sample size
#' purely through the combination of the true effect and sampling noise.
#'
#' Returns NULL if fewer than 100 valid replications were achieved
#' (indicating a near-degenerate parameter combination).
#'
#' @param cond_id   Integer. Row index into params_df identifying
#'                  which parameter combination to simulate.
#' @param params_df Data frame. The full parameter grid, with columns
#'                  including n_per_group, ctrl_mean, ctrl_sd,
#'                  treat_mean, treat_sd, scale_min, scale_max,
#'                  direction, and condition_id.
#' @param n_reps    Integer. Number of Monte Carlo replications.
#'
#' @return A single-row tibble with columns: condition_id,
#'         observed_d_mean, observed_d_sd, observed_d_p05,
#'         observed_d_p95, observed_d_p99, observed_d_max, n_valid.
#'         Returns NULL if < 100 valid replications.
run_condition <- function(cond_id, params_df, n_reps) {
  p <- params_df |> filter(condition_id == cond_id)
  
  ds <- map_dbl(seq_len(n_reps), \(r) {
    sim_one_rep(r,
                n_per      = p$n_per_group,
                ctrl_mean  = p$ctrl_mean,
                ctrl_sd    = p$ctrl_sd,
                treat_mean = p$treat_mean,
                treat_sd   = p$treat_sd,
                scale_min  = p$scale_min,
                scale_max  = p$scale_max,
                direction  = p$dir_code)
  })
  
  ds <- ds[!is.na(ds)]
  if (length(ds) < 100) return(NULL)
  
  tibble(
    condition_id    = cond_id,
    observed_d_mean = mean(ds),
    observed_d_sd   = sd(ds),
    observed_d_p05  = quantile(ds, 0.05),
    observed_d_p95  = quantile(ds, 0.95),
    observed_d_p99  = quantile(ds, 0.99),
    observed_d_max  = max(ds),
    n_valid         = length(ds)
  )
}

```

# Scale archetypes

```{r}

scales <- tribble(
  ~scale_type,          ~scale_name,            ~scale_min, ~scale_max, ~ctrl_mean, ~ctrl_sd,
  "symptom_clinical",   "BDI-II (clinical)",     0,         63,         25,         10.0,
  "symptom_clinical",   "PHQ-9 (clinical)",      0,         27,         14,          5.5,
  "symptom_community",  "PHQ-9 (community)",     0,         27,          3,          3.6,
  "symptom_community",  "BDI-II (community)",    0,         63,          8,          8.5,
  "symptom_clinical",   "CES-D (clinical)",      0,         60,         24,         10.0,
  "symptom_community",  "CES-D (community)",     0,         60,          9,          8.2,
  "wellbeing",          "SWLS",                  5,         35,         20,          6.2,
  "wellbeing",          "RSES (0-30)",           0,         30,         16,          5.3,
  "trait",              "PANAS-PA",             10,         50,         32,          7.0,
  "trait",              "STAI-Trait",           20,         80,         38,          9.8,
  "wellbeing",          "PSS-10",                0,         40,         17,          6.2,
  "trait",              "NEO-FFI Neuroticism",   0,         48,         19,          7.7,
) |>
  mutate(
    range      = scale_max - scale_min,
    range_sd   = range / ctrl_sd,
    avail_down = ctrl_mean - scale_min,
    avail_up   = scale_max - ctrl_mean
  )

scales |>
  mutate(scale_name = fct_reorder(scale_name, range_sd)) |>
  ggplot(aes(range_sd, scale_name)) +
  geom_vline(aes(xintercept = mean(range_sd)), linetype = "dotted") +
  geom_point() +
  scale_x_continuous(breaks = scales::breaks_pretty(n = 6),
                     name = "Max possible scale range as a proportion of SD") +
  theme_linedraw()

```

## Illustrating the scale archetypes

The plots below show the control group score distributions implied by each scale archetype. These are the beta distributions that `rbounded()` generates, rescaled to each scale's range. The key visual takeaway is how differently the four scale types distribute scores within their bounds — and therefore how much room exists for a treatment effect to shift the mean.

### Control group distributions by scale type

Each density curve shows the population distribution of scores in the control (untreated) group for one scale archetype. The vertical dashed line marks the control mean; the shaded region shows ±1 SD. Scales are grouped by type: symptom scales pile up near the floor (especially in community samples), while trait and well-being scales spread more evenly across the range.

```{r fig.width=12, fig.height=8}

# Generate theoretical beta densities for each scale's control group
density_data <- scales |>
  mutate(
    # Beta parameters for control group
    mu    = (ctrl_mean - scale_min) / range,
    sigma = ctrl_sd / range,
    var_  = sigma^2,
    phi   = mu * (1 - mu) / var_ - 1,
    a     = mu * phi,
    b     = (1 - mu) * phi
  ) |>
  filter(a > 0.01, b > 0.01) |>
  # Generate density curves on original scale
  rowwise() |>
  mutate(
    dens = list({
      x_unit <- seq(0.001, 0.999, length.out = 500)
      x_raw  <- x_unit * range + scale_min
      y      <- dbeta(x_unit, a, b) / range  # rescale density to original units
      tibble(x = x_raw, y = y)
    })
  ) |>
  ungroup() |>
  unnest(dens)

density_data |>
  mutate(
    scale_type_label = scale_type_labels[scale_type],
    scale_type_label = factor(scale_type_label, levels = scale_type_labels)
  ) |>
  ggplot(aes(x = x, y = y)) +
  geom_area(aes(fill = scale_type), alpha = 0.25) +
  geom_line(aes(colour = scale_type), linewidth = 0.7) +
  # Mean marker
  geom_vline(
    data = scales |> mutate(
      scale_type_label = factor(scale_type_labels[scale_type], levels = scale_type_labels)
    ),
    aes(xintercept = ctrl_mean, colour = scale_type),
    linetype = "dashed", linewidth = 0.6
  ) +
  # Scale boundaries as solid vertical lines
  geom_vline(
    data = scales |> mutate(
      scale_type_label = factor(scale_type_labels[scale_type], levels = scale_type_labels)
    ),
    aes(xintercept = scale_min), colour = "grey30", linewidth = 0.3
  ) +
  geom_vline(
    data = scales |> mutate(
      scale_type_label = factor(scale_type_labels[scale_type], levels = scale_type_labels)
    ),
    aes(xintercept = scale_max), colour = "grey30", linewidth = 0.3
  ) +
  facet_wrap(~ scale_name, scales = "free", ncol = 4) +
  scale_colour_manual(values = scale_type_colours, labels = scale_type_labels, aesthetics = c("colour", "fill")) +
  labs(
    title    = "Control group score distributions for each scale archetype",
    subtitle = "Dashed line = control mean; vertical grey lines = scale boundaries. Note the x-axis varies by scale.",
    x = "Score",
    y = "Density",
    colour = "Scale type",
    fill   = "Scale type"
  )

```

### Comparing one scale per type on a common 0–1 axis

To make the distributional shapes directly comparable, we can rescale all scores to the unit interval (0 = scale minimum, 1 = scale maximum). This reveals the key structural difference: symptom scales in community samples are sharply right-skewed with most mass near zero, while trait scales are more symmetric and centred.

```{r fig.width=10, fig.height=5}

# Pick one representative scale per type
representative_scales <- c(
  "symptom_clinical"  = "BDI-II (clinical)",
  "symptom_community" = "PHQ-9 (community)",
  "trait"             = "STAI-Trait",
  "wellbeing"         = "SWLS"
)

rep_scales_df <- scales |>
  filter(scale_name %in% representative_scales) |>
  mutate(
    mu    = (ctrl_mean - scale_min) / range,
    sigma = ctrl_sd / range,
    var_  = sigma^2,
    phi   = mu * (1 - mu) / var_ - 1,
    a     = mu * phi,
    b     = (1 - mu) * phi
  )

unit_density <- rep_scales_df |>
  rowwise() |>
  mutate(
    dens = list({
      x <- seq(0.001, 0.999, length.out = 500)
      y <- dbeta(x, a, b)
      tibble(x_unit = x, y = y)
    })
  ) |>
  ungroup() |>
  unnest(dens)

unit_density |>
  ggplot(aes(x = x_unit, y = y, colour = scale_name, fill = scale_name)) +
  geom_area(alpha = 0.12, position = "identity") +
  geom_line(linewidth = 0.9) +
  geom_vline(
    data = rep_scales_df,
    aes(xintercept = mu, colour = scale_name),
    linetype = "dashed", linewidth = 0.5
  ) +
  scale_x_continuous(labels = scales::percent_format(), breaks = seq(0, 1, 0.2)) +
  labs(
    title    = "Control group distributions on a common 0–1 scale",
    subtitle = "One representative scale per type; dashed = mean position within scale range",
    x = "Position within scale range (0 = minimum, 1 = maximum)",
    y = "Density",
    colour = "Scale",
    fill   = "Scale"
  )

```

### How treatment shifts and compresses the distribution

For each representative scale, the plot below shows how the treatment group distribution shifts and compresses in *both* directions (decrease toward floor = red tones, increase toward ceiling = blue tones) at 30%, 60%, and 90% of available room. The control distribution is shown in grey. The asymmetry is striking: for a community symptom scale like the PHQ-9, there is almost no room to decrease but lots of room to increase.

```{r fig.width=12, fig.height=7}

# For each representative scale, generate treatment densities in both directions
effect_levels <- c(0.3, 0.6, 0.9)

shift_data <- rep_scales_df |>
  crossing(
    effect_proportion = effect_levels,
    direction = c("decrease", "increase")
  ) |>
  mutate(
    avail       = if_else(direction == "decrease",
                          ctrl_mean - scale_min,
                          scale_max - ctrl_mean),
    treat_mean  = if_else(direction == "decrease",
                          ctrl_mean - effect_proportion * avail,
                          ctrl_mean + effect_proportion * avail),
    dist_to_bnd = if_else(direction == "decrease",
                          treat_mean - scale_min,
                          scale_max - treat_mean),
    treat_sd    = ctrl_sd * sqrt(dist_to_bnd / avail),
    # Beta parameters for treatment group
    t_mu    = (treat_mean - scale_min) / range,
    t_sigma = treat_sd / range,
    t_var   = t_sigma^2,
    t_phi   = t_mu * (1 - t_mu) / t_var - 1,
    t_a     = t_mu * t_phi,
    t_b     = (1 - t_mu) * t_phi
  ) |>
  filter(t_a > 0.01, t_b > 0.01, !is.na(treat_sd), treat_sd >= 0.5)

# Add control row (direction-neutral)
ctrl_row <- rep_scales_df |>
  mutate(
    effect_proportion = 0,
    direction = "control",
    treat_mean = ctrl_mean,
    treat_sd = ctrl_sd,
    t_mu = mu, t_sigma = sigma, t_var = var_,
    t_phi = phi, t_a = a, t_b = b,
    avail = NA_real_, dist_to_bnd = NA_real_
  )

shift_all <- bind_rows(shift_data, ctrl_row)

shift_densities <- shift_all |>
  rowwise() |>
  mutate(
    dens = list({
      x_raw <- seq(scale_min + 0.01, scale_max - 0.01, length.out = 500)
      x_unit <- (x_raw - scale_min) / range
      y <- dbeta(x_unit, t_a, t_b) / range
      tibble(x = x_raw, y = y)
    })
  ) |>
  ungroup() |>
  unnest(dens) |>
  mutate(
    ep_label = case_when(
      direction == "control"  ~ "Control",
      direction == "decrease" ~ paste0("Decrease ", effect_proportion * 100, "%"),
      direction == "increase" ~ paste0("Increase ", effect_proportion * 100, "%")
    ),
    ep_label = fct_relevel(ep_label, "Decrease 90%", "Decrease 60%", "Decrease 30%",
                           "Control", "Increase 30%", "Increase 60%", "Increase 90%")
  )

shift_colours <- c(
  "Decrease 90%" = "#b2182b", "Decrease 60%" = "#d6604d", "Decrease 30%" = "#f4a582",
  "Control"      = "grey40",
  "Increase 30%" = "#92c5de", "Increase 60%" = "#4393c3", "Increase 90%" = "#2166ac"
)

shift_densities |>
  ggplot(aes(x = x, y = y, colour = ep_label, fill = ep_label)) +
  geom_area(alpha = 0.08, position = "identity") +
  geom_line(linewidth = 0.7) +
  facet_wrap(~ scale_name, scales = "free", ncol = 2) +
  scale_colour_manual(values = shift_colours) +
  scale_fill_manual(values = shift_colours) +
  labs(
    title    = "Treatment shifts in both directions: decrease (red) and increase (blue)",
    subtitle = "Control in grey; 30/60/90% of available room. Note the asymmetry in available room.",
    x = "Score",
    y = "Density",
    colour = NULL,
    fill   = NULL
  )

```

### Available room for effect: a visual summary

This plot summarises the geometry that drives the simulation. For each scale, the full scoring range is shown on a normalised 0–1 axis. The black tick marks the control mean. Room to *decrease* scores (toward the floor) is shown in red to the left; room to *increase* scores (toward the ceiling) is shown in blue to the right. The max plausible SMD depends on which direction the intervention moves — the simulation covers both.

```{r fig.width=10, fig.height=7}

avail_plot_data <- scales |>
  mutate(
    ctrl_prop  = (ctrl_mean - scale_min) / range,
    down_prop  = avail_down / range,
    up_prop    = avail_up / range,
    scale_name = fct_reorder(scale_name, ctrl_prop)
  )

avail_plot_data |>
  ggplot(aes(y = scale_name)) +
  # Full range background
  geom_segment(aes(x = 0, xend = 1, yend = scale_name),
               colour = "grey85", linewidth = 7) +
  # Room to decrease (left of mean, toward floor)
  geom_segment(aes(x = 0, xend = ctrl_prop, yend = scale_name),
               colour = "#d62728", linewidth = 7, alpha = 0.35) +
  # Room to increase (right of mean, toward ceiling)
  geom_segment(aes(x = ctrl_prop, xend = 1, yend = scale_name),
               colour = "#1f77b4", linewidth = 7, alpha = 0.35) +
  # Control mean marker
  geom_point(aes(x = ctrl_prop), shape = "|", size = 5, colour = "black") +
  # Arrows in both directions
  geom_segment(
    aes(x = ctrl_prop, xend = pmax(ctrl_prop - down_prop * 0.8, 0.01), yend = scale_name),
    arrow = arrow(length = unit(0.12, "cm"), type = "closed"),
    colour = "#d62728", linewidth = 0.5
  ) +
  geom_segment(
    aes(x = ctrl_prop, xend = pmin(ctrl_prop + up_prop * 0.8, 0.99), yend = scale_name),
    arrow = arrow(length = unit(0.12, "cm"), type = "closed"),
    colour = "#1f77b4", linewidth = 0.5
  ) +
  # Percentage labels
  geom_text(aes(x = -0.02, label = sprintf("↓%.0f%%", down_prop * 100)),
            hjust = 1, size = 2.8, colour = "#d62728") +
  geom_text(aes(x = 1.02, label = sprintf("↑%.0f%%", up_prop * 100)),
            hjust = 0, size = 2.8, colour = "#1f77b4") +
  scale_x_continuous(labels = scales::percent_format(), limits = c(-0.12, 1.12),
                     breaks = seq(0, 1, 0.25)) +
  labs(
    title    = "Available room for treatment effects: both directions",
    subtitle = "Red (left) = room to decrease scores; blue (right) = room to increase. Black tick = control mean.",
    x = "Position within scale range",
    y = NULL
  )

```

# Build full parameter grid

The simulation varies four factors in a fully crossed design:

- **Scale archetype** (12 levels): determines the scale range, control mean, and control SD.
- **Direction** (2 levels: decrease, increase): whether the treatment moves scores toward the floor or ceiling. This is crossed with every scale, because the same measure can be used in studies aiming to increase or decrease scores, and the available room differs dramatically by direction.
- **Effect proportion** (9 levels: 0.1 to 0.9 in steps of 0.1): the proportion of the *available room* between the control mean and the target boundary that the treatment mean moves.
- **Sample size per group** (9 levels: 10 to 200): captures the range of sample sizes commonly seen in psychological intervention studies.

For each combination, the treatment group SD is computed using the square-root compression model described above. Conditions where the available room is too small to produce a valid beta distribution (e.g., decreasing PHQ-9 community scores at high effect proportions) are automatically filtered out.

```{r}

params <- scales |>
  crossing(
    direction         = c("decrease", "increase"),
    effect_proportion = seq(0.1, 0.9, by = 0.1),
    n_per_group       = c(10, 15, 20, 25, 30, 40, 50, 100, 200)
  ) |>
  mutate(
    avail = if_else(direction == "decrease", avail_down, avail_up),
    treat_mean = if_else(direction == "decrease",
                         ctrl_mean - effect_proportion * avail,
                         ctrl_mean + effect_proportion * avail),
    dist_to_bound = if_else(direction == "decrease",
                            treat_mean - scale_min,
                            scale_max - treat_mean),
    treat_sd = ctrl_sd * sqrt(dist_to_bound / avail),
    # internal direction code for sim_one_rep
    dir_code = if_else(direction == "decrease", "down", "up")
  ) |>
  filter(!is.na(treat_sd), treat_sd >= 0.5, avail >= 0.5) |>
  mutate(
    pooled_sd_approx = sqrt((ctrl_sd^2 + treat_sd^2) / 2),
    true_d           = abs(treat_mean - ctrl_mean) / pooled_sd_approx,
    condition_id     = row_number()
  )

cat(sprintf("Total conditions: %d (%d decrease, %d increase)\n",
            nrow(params),
            sum(params$direction == "decrease"),
            sum(params$direction == "increase")))

```

# Run simulation in parallel

```{r}

n_reps <- 10000

cat(sprintf("Parameter grid: %d conditions x %d reps = %d total sims\n",
            nrow(params), n_reps, nrow(params) * n_reps))

cat("Running simulation with", availableCores() - 1, "workers...\n")


if(file.exists("results.rds") && "direction" %in% names(read_rds("results.rds"))){
  results <- read_rds("results.rds")
} else {
  sim_results <- future_map(
    params$condition_id,
    \(cid) run_condition(cid, params, n_reps),
    .options = furrr_options(seed = TRUE),
    .progress = TRUE
  ) |>
    compact() |>
    list_rbind()
  
  # Join back to parameters
  results <- params |>
    inner_join(sim_results, by = "condition_id")
  
  write_rds(results, "results.rds")
}

cat(sprintf("\nSimulation complete: %d conditions with valid results\n", nrow(results)))

```

# Analysis

## Max achievable d per scale and direction

### N = 200

At the largest simulated sample size (N = 200 per group), what is the maximum mean and P95 Cohen's *d* achievable on each scale, separately for interventions that increase vs decrease scores?

```{r}

max_per_scale <- results |>
  filter(n_per_group == 200) |>
  group_by(scale_name, scale_type, direction, range, range_sd) |>
  summarise(
    max_true_d = max(true_d),
    max_mean_d = max(observed_d_mean),
    max_p95_d  = max(observed_d_p95),
    multiplier = max(observed_d_mean) / first(range_sd),
    mult_p95   = max(observed_d_p95) / first(range_sd),
    .groups = "drop"
  ) |>
  arrange(desc(max_p95_d))

max_per_scale |>
  print(n = 30, width = 150)

```

```{r fig.width=10, fig.height=8}

max_per_scale |>
  mutate(
    label = paste0(scale_name, " (", direction, ")"),
    label = fct_reorder(label, max_p95_d)
  ) |>
  ggplot(aes(y = label)) +
  # P95 bar (full extent)
  geom_col(aes(x = max_p95_d, fill = scale_type), alpha = 0.4, width = 0.7) +
  # Mean d bar (inner, darker)
  geom_col(aes(x = max_mean_d, fill = scale_type), width = 0.5) +
  # Labels
  geom_text(aes(x = max_p95_d, label = sprintf("%.1f", max_p95_d)),
            hjust = -0.15, size = 3, colour = "grey30") +
  geom_text(aes(x = max_mean_d, label = sprintf("%.1f", max_mean_d)),
            hjust = 1.15, size = 2.8, colour = "white", fontface = "bold") +
  scale_fill_manual(values = scale_type_colours, labels = scale_type_labels) +
  labs(
    title    = "Maximum achievable SMD per scale and direction (N = 200 per group)",
    subtitle = "Dark bar = mean d; light extension = 95th percentile observed d",
    x = "Cohen's d",
    y = NULL,
    fill = "Scale type"
  ) +
  coord_cartesian(xlim = c(0, max(max_per_scale$max_p95_d) * 1.12))

```

### N = 25

At a typical sample size (N = 25 per group), what is the maximum mean and P95 Cohen's *d* achievable on each scale?

```{r}

max_per_scale2 <- results |>
  filter(n_per_group == 25) |>
  group_by(scale_name, scale_type, direction, range, range_sd) |>
  summarise(
    max_true_d = max(true_d),
    max_mean_d = max(observed_d_mean),
    max_p95_d  = max(observed_d_p95),
    multiplier = max(observed_d_mean) / first(range_sd),
    mult_p95   = max(observed_d_p95) / first(range_sd),
    .groups = "drop"
  ) |>
  arrange(desc(max_p95_d))

max_per_scale2 |>
  print(n = 30, width = 150)

```

```{r fig.width=10, fig.height=8}

max_per_scale2 |>
  mutate(
    label = paste0(scale_name, " (", direction, ")"),
    label = fct_reorder(label, max_p95_d)
  ) |>
  ggplot(aes(y = label)) +
  # P95 bar (full extent)
  geom_col(aes(x = max_p95_d, fill = scale_type), alpha = 0.4, width = 0.7) +
  # Mean d bar (inner, darker)
  geom_col(aes(x = max_mean_d, fill = scale_type), width = 0.5) +
  # Labels
  geom_text(aes(x = max_p95_d, label = sprintf("%.1f", max_p95_d)),
            hjust = -0.15, size = 3, colour = "grey30") +
  geom_text(aes(x = max_mean_d, label = sprintf("%.1f", max_mean_d)),
            hjust = 1.15, size = 2.8, colour = "white", fontface = "bold") +
  scale_fill_manual(values = scale_type_colours, labels = scale_type_labels) +
  labs(
    title    = "Maximum achievable SMD per scale and direction (N = 25 per group)",
    subtitle = "Dark bar = mean d; light extension = 95th percentile observed d",
    x = "Cohen's d",
    y = NULL,
    fill = "Scale type"
  ) +
  coord_cartesian(xlim = c(0, max(max_per_scale$max_p95_d) * 1.12))

```

## Max P95 d by scale, direction, and N

The maximum P95 observed *d* across all effect proportions, for each scale, direction, and sample size. This is the answer to: "what is the largest *d* a study of this size could plausibly report on this measure, given the direction of effect?"

```{r}

max_by_n <- results |>
  group_by(scale_name, scale_type, direction, range_sd, n_per_group) |>
  summarise(
    max_mean_d = max(observed_d_mean),
    max_p95_d  = max(observed_d_p95),
    max_p99_d  = max(observed_d_p99),
    .groups = "drop"
  )

max_by_n |>
  select(scale_name, direction, range_sd, n_per_group, max_p95_d) |>
  pivot_wider(names_from = n_per_group, values_from = max_p95_d, names_prefix = "n_") |>
  arrange(direction, desc(range_sd)) |>
  print(n = 30, width = 150)

```

```{r fig.width=12, fig.height=7}

max_by_n |>
  mutate(
    label = paste0(scale_name, " (", direction, ")"),
    label = fct_reorder(label, max_p95_d, .fun = max)
  ) |>
  ggplot(aes(x = n_per_group, y = max_p95_d, colour = label, linetype = direction)) +
  geom_line(linewidth = 0.7) +
  geom_point(size = 1.5) +
  facet_wrap(~ scale_type, scales = "free_y",
             labeller = labeller(scale_type = scale_type_labels)) +
  scale_x_continuous(trans = "log10", breaks = c(10, 20, 50, 100, 200)) +
  scale_linetype_manual(values = c("decrease" = "solid", "increase" = "dashed")) +
  labs(
    title    = "Maximum P95 observed d by sample size and direction",
    subtitle = "Solid = decrease; dashed = increase. Faceted by scale type.",
    x = "N per group (log scale)",
    y = "Max P95 observed d",
    colour = "Scale × direction",
    linetype = "Direction"
  ) +
  theme(legend.position = "right", legend.text = element_text(size = 7))

```

## P95 multiplier by scale type, direction, and N

The multiplier converts the naive Range/SD ratio to the maximum plausible P95 *d*. Shown separately for each direction.

```{r}

mult_summary <- max_by_n |>
  mutate(mult_p95 = max_p95_d / range_sd) |>
  group_by(scale_type, direction, n_per_group) |>
  summarise(
    mean_mult_p95 = mean(mult_p95),
    .groups = "drop"
  )

mult_summary |>
  pivot_wider(names_from = n_per_group, values_from = mean_mult_p95, names_prefix = "n_") |>
  arrange(direction, scale_type) |>
  print(n = 20, width = 120)

```

```{r fig.width=10, fig.height=5}

mult_summary |>
  ggplot(aes(x = n_per_group, y = mean_mult_p95, colour = scale_type,
             linetype = direction)) +
  geom_line(linewidth = 1) +
  geom_point(aes(shape = direction), size = 2.5) +
  scale_x_continuous(trans = "log10", breaks = c(10, 20, 50, 100, 200)) +
  scale_colour_manual(values = scale_type_colours, labels = scale_type_labels) +
  scale_linetype_manual(values = c("decrease" = "solid", "increase" = "dashed")) +
  scale_shape_manual(values = c("decrease" = 16, "increase" = 17)) +
  labs(
    title    = "P95 Multiplier: Range/SD ratio → max plausible SMD",
    subtitle = "Solid/circle = decrease; dashed/triangle = increase",
    x = "N per group (log scale)",
    y = "Multiplier (max P95 d / Range:SD)",
    colour   = "Scale type",
    linetype = "Direction",
    shape    = "Direction"
  ) +
  coord_cartesian(ylim = c(0, NA))

```

## Red flag thresholds

The most practically useful output: the maximum P95 *d* one should expect by scale type, direction, and sample size. An observed *d* above these curves should be treated with suspicion. Note the dramatic asymmetry: community symptom scales have a tiny ceiling for *decreasing* effects but a much higher ceiling for *increasing* effects.

```{r}

red_flag <- max_by_n |>
  group_by(scale_type, direction, n_per_group) |>
  summarise(
    mean_p95 = mean(max_p95_d),
    min_p95  = min(max_p95_d),
    max_p95  = max(max_p95_d),
    .groups = "drop"
  )

red_flag |>
  print(n = 30, width = 120)

```

```{r fig.width=10, fig.height=5}

red_flag |>
  ggplot(aes(x = n_per_group, colour = scale_type, fill = scale_type,
             linetype = direction)) +
  geom_ribbon(aes(ymin = min_p95, ymax = max_p95, group = interaction(scale_type, direction)),
              alpha = 0.1, colour = NA) +
  geom_line(aes(y = mean_p95), linewidth = 1.2) +
  geom_point(aes(y = mean_p95, shape = direction), size = 2.5) +
  scale_x_continuous(trans = "log10", breaks = c(10, 20, 50, 100, 200)) +
  scale_colour_manual(values = scale_type_colours, labels = scale_type_labels) +
  scale_fill_manual(values = scale_type_colours, labels = scale_type_labels) +
  scale_linetype_manual(values = c("decrease" = "solid", "increase" = "dashed")) +
  scale_shape_manual(values = c("decrease" = 16, "increase" = 17)) +
  geom_hline(yintercept = 2.0, linetype = "dotted", colour = "grey50") +
  annotate("text", x = 180, y = 2.2, label = "d = 2.0", colour = "grey50", size = 3.5) +
  labs(
    title    = "Red flag thresholds: max plausible P95 observed d",
    subtitle = "Solid/circle = decrease; dashed/triangle = increase. Band = range across scales within type.",
    x = "N per group (log scale)",
    y = "Max plausible P95 SMD",
    colour = "Scale type",
    fill   = "Scale type",
    linetype = "Direction",
    shape    = "Direction"
  ) +
  coord_cartesian(ylim = c(0, NA))

```

## Effect size ramp

How does the P95 observed *d* grow as the treatment effect increases? Shown for selected scales at small (N = 20), medium (N = 50), and large (N = 200) sample sizes. Results are now faceted by scale × direction.

```{r fig.width=14, fig.height=10}

selected_scales <- c("PHQ-9 (clinical)", "BDI-II (clinical)", "SWLS",
                      "STAI-Trait", "PHQ-9 (community)", "CES-D (community)")

results |>
  filter(
    scale_name %in% selected_scales,
    n_per_group %in% c(20, 50, 200)
  ) |>
  mutate(
    n_label    = paste("N =", n_per_group),
    n_label    = fct_reorder(n_label, n_per_group),
    facet_label = paste0(scale_name, " (", direction, ")"),
    scale_name_f = factor(scale_name, levels = selected_scales)
  ) |>
  ggplot(aes(x = effect_proportion, colour = n_label, fill = n_label)) +
  geom_ribbon(aes(ymin = observed_d_p95, ymax = observed_d_p99), alpha = 0.12, colour = NA) +
  geom_line(aes(y = observed_d_p95), linewidth = 1) +
  geom_point(aes(y = observed_d_p95), size = 1.5) +
  geom_line(aes(y = observed_d_mean), linewidth = 0.5, linetype = "dotted", alpha = 0.5) +
  facet_grid(direction ~ scale_name_f, scales = "free_y") +
  scale_colour_brewer(palette = "Set1") +
  scale_fill_brewer(palette = "Set1") +
  labs(
    title    = "P95 observed d as treatment effect proportion increases",
    subtitle = "Solid = P95; dotted = mean d; shaded band = P95 to P99. Rows = direction.",
    x = "Effect proportion (fraction of available room used)",
    y = "Cohen's d",
    colour = "Sample size",
    fill   = "Sample size"
  )

```

## Small-sample noise inflation

How much does small N inflate the *observed* d beyond the true population value? Panel A shows the SD of the sampling distribution of *d* at the maximum effect level. Panel B shows the P95/mean ratio: the factor by which a "lucky" study overestimates the true *d*.

```{r fig.width=10, fig.height=5}

# At max effect proportion per scale × direction
max_props <- results |>
  filter(n_per_group == 200) |>
  group_by(scale_name, direction) |>
  summarise(max_ep = max(effect_proportion), .groups = "drop")

noise_data <- results |>
  inner_join(max_props, by = c("scale_name", "direction")) |>
  filter(effect_proportion == max_ep)

p_a <- noise_data |>
  filter(scale_name %in% selected_scales) |>
  mutate(label = paste0(scale_name, " (", direction, ")")) |>
  ggplot(aes(x = n_per_group, y = observed_d_sd,
             colour = scale_type, linetype = direction, group = label)) +
  geom_line(linewidth = 0.8) +
  geom_point(size = 2) +
  scale_x_continuous(trans = "log10", breaks = c(10, 20, 50, 100, 200)) +
  scale_colour_manual(values = scale_type_colours, labels = scale_type_labels) +
  scale_linetype_manual(values = c("decrease" = "solid", "increase" = "dashed")) +
  labs(
    title = "A. Sampling variability of d",
    x = "N per group", y = "SD of observed d",
    colour = "Scale type", linetype = "Direction"
  ) +
  theme(legend.position = "none")

p_b <- noise_data |>
  filter(scale_name %in% selected_scales) |>
  mutate(
    inflation = observed_d_p95 / observed_d_mean,
    label = paste0(scale_name, " (", direction, ")")
  ) |>
  ggplot(aes(x = n_per_group, y = inflation,
             colour = scale_type, linetype = direction, group = label)) +
  geom_line(linewidth = 0.8) +
  geom_point(size = 2) +
  geom_hline(yintercept = 1.0, linetype = "dotted", colour = "grey50") +
  scale_x_continuous(trans = "log10", breaks = c(10, 20, 50, 100, 200)) +
  scale_colour_manual(values = scale_type_colours, labels = scale_type_labels) +
  scale_linetype_manual(values = c("decrease" = "solid", "increase" = "dashed")) +
  labs(
    title = "B. P95 / Mean d ratio",
    x = "N per group", y = "P95 / Mean ratio",
    colour = "Scale type", linetype = "Direction"
  )

# Combine
library(patchwork)
p_a + p_b +
  plot_annotation(
    title    = "Small-sample noise inflation of observed SMDs",
    subtitle = "Solid = decrease; dashed = increase. At max simulated effect level."
  ) +
  plot_layout(guides = "collect") &
  theme(legend.position = "right")

```

## Stacked bar comparison across N

A direct comparison of mean *d*, P95, and P99 for each scale × direction at three representative sample sizes.

```{r fig.width=16, fig.height=10}

max_by_n |>
  filter(n_per_group %in% c(20, 50, 200)) |>
  mutate(
    label   = paste0(scale_name, " (", direction, ")"),
    label   = fct_reorder(label, max_p95_d, .fun = max),
    n_label = paste("N =", n_per_group),
    n_label = fct_reorder(n_label, n_per_group)
  ) |>
  ggplot(aes(y = label)) +
  # P99 bar (lightest, full extent)
  geom_col(aes(x = max_p99_d, fill = scale_type), width = 0.7, alpha = 0.2) +
  # P95 bar (medium)
  geom_col(aes(x = max_p95_d, fill = scale_type), width = 0.7, alpha = 0.5) +
  # Mean d bar (darkest, innermost)
  geom_col(aes(x = max_mean_d, fill = scale_type), width = 0.7, alpha = 1.0) +
  # Value labels
  geom_text(aes(x = max_p99_d,
                label = sprintf("%.1f | %.1f | %.1f", max_mean_d, max_p95_d, max_p99_d)),
            hjust = -0.05, size = 2, colour = "grey40") +
  facet_wrap(~ n_label, ncol = 3) +
  scale_fill_manual(values = scale_type_colours, labels = scale_type_labels) +
  labs(
    title    = "Maximum plausible SMDs: mean d, P95, and P99",
    subtitle = "Darkest = mean d; medium = P95; lightest = P99. Labels show mean | P95 | P99.",
    x = "Cohen's d",
    y = NULL,
    fill = "Scale type"
  ) +
  coord_cartesian(xlim = c(0, max(max_by_n$max_p99_d) * 1.3))

```

## Range/SD ratio vs max plausible d

The relationship between a scale's Range/SD ratio and its maximum plausible P95 *d*, with direction encoded as shape. This demonstrates that the Range/SD ratio alone is insufficient — both the scale type and the *direction* of the intervention fundamentally determine the achievable ceiling.

```{r fig.width=10, fig.height=7}

max_by_n |>
  filter(n_per_group %in% c(20, 50, 200)) |>
  mutate(n_label = paste("N =", n_per_group)) |>
  ggplot(aes(x = range_sd, y = max_p95_d, colour = scale_type,
             shape = direction)) +
  geom_point(size = 3, alpha = 0.7) +
  # Reference lines for multipliers
  geom_abline(slope = 0.15, intercept = 0, linetype = "dotted",  colour = "grey60") +
  geom_abline(slope = 0.35, intercept = 0, linetype = "dotted",  colour = "grey60") +
  geom_abline(slope = 0.55, intercept = 0, linetype = "solid",   colour = "grey60", linewidth = 0.3) +
  geom_abline(slope = 0.75, intercept = 0, linetype = "dotted",  colour = "grey60") +
  geom_abline(slope = 0.95, intercept = 0, linetype = "dotted",  colour = "grey60") +
  # Multiplier labels
  annotate("text", x = 7.6, y = 0.15 * 7.6 + 0.15, label = "×0.15", colour = "grey50", size = 3) +
  annotate("text", x = 7.6, y = 0.35 * 7.6 + 0.15, label = "×0.35", colour = "grey50", size = 3) +
  annotate("text", x = 7.6, y = 0.55 * 7.6 + 0.15, label = "×0.55", colour = "grey50", size = 3) +
  annotate("text", x = 7.6, y = 0.75 * 7.6 + 0.15, label = "×0.75", colour = "grey50", size = 3) +
  annotate("text", x = 7.6, y = 0.95 * 7.6 + 0.15, label = "×0.95", colour = "grey50", size = 3) +
  scale_colour_manual(values = scale_type_colours, labels = scale_type_labels) +
  scale_shape_manual(values = c("decrease" = 16, "increase" = 17)) +
  facet_wrap(~ n_label) +
  labs(
    title    = "Range/SD ratio vs maximum plausible P95 observed d",
    subtitle = "Circle = decrease; triangle = increase. Same Range/SD → very different ceilings by direction.",
    x = "Range / SD ratio",
    y = "Max P95 observed d",
    colour = "Scale type",
    shape  = "Direction"
  )

```

```{r}

# write_csv(results, "max_smd_simulation_results.csv")
# write_csv(max_by_n, "max_smd_by_scale_and_n.csv")

```
