---
title: "Assessing the maxrange to SD ratio"
subtitle: "Bainbridge et al.'s data"
author: "Ian Hussey"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

```{r, include=FALSE}
knitr::opts_chunk$set(message=FALSE,
                      warning=FALSE)
```

# Dependencies

```{r}

library(tidyverse)
library(scales)
library(knitr)
library(kableExtra)
library(betareg)
library(ggrepel)
library(arrow)

source("beta_smd_bounds.R")

```

# Get data

```{r}

dat_bainbridge <- read_csv("../../../data/bainbridge et al/processed/data_processed_itemlevel_long.csv") |>
  mutate(min_response = 1,
         max_response = 5) |>
  mutate(scale = case_when(
    scale == "BFI_personality" & subscale == "o" ~ "bfi openness",
    scale == "BFI_personality" & subscale == "c" ~ "bfi conscientiousness",
    scale == "BFI_personality" & subscale == "e" ~ "bfi extraversion",
    scale == "BFI_personality" & subscale == "a" ~ "bfi agreeableness",
    scale == "BFI_personality" & subscale == "n" ~ "bfi neuroticism",
    TRUE ~ scale  # Keeps the original value if conditions aren't met
  )) |>
  mutate(scale = case_when(
    scale == "IPIP_personality" & subscale == "o" ~ "ipip openness",
    scale == "IPIP_personality" & subscale == "c" ~ "ipip conscientiousness",
    scale == "IPIP_personality" & subscale == "e" ~ "ipip extraversion",
    scale == "IPIP_personality" & subscale == "a" ~ "ipip agreeableness",
    scale == "IPIP_personality" & subscale == "n" ~ "ipip neuroticism",
    TRUE ~ scale  # Keeps the original value if conditions aren't met
  ))

dat_poopchoc <- read_csv("../../../data/not-so-simple-preferences/data_processed_after_exclusions.csv")  |>
  mutate(min_response = 1, 
         max_response = 7) |> # not so simple preferences study (not bainbridge)
  select(id = participant_id,
         min_response,
         max_response,
         poop = classic_poop, 
         chocolate = classic_chocolate,
         pedophile, love, murder, vacation, racist, 
         honest, dishonest, 
         girls_skirts, boys_skirts, cats_legs, fish_legs,
         attention_check1_numeric, 
         attention_check2_numeric) |>
  pivot_longer(cols = c(-id, -min_response, -max_response),
               names_to = "scale",
               values_to = "response") |>
  mutate(subscale = scale)


dat_brysbaert_long      <- read_parquet("../../../data/brysbaert et al 2024/processed/dat_long_brysbaert.parquet")

dat <- dat_bainbridge |>
  bind_rows(dat_poopchoc) |>
  bind_rows(dat_brysbaert_long)

```

# n participants in datasets

```{r}

data_s1 <- read_csv("../../../data/bainbridge et al/raw/s1.csv")
data_s2 <- read_csv("../../../data/bainbridge et al/raw/s2.csv")
data_s3 <- read_csv("../../../data/bainbridge et al/raw/s3.csv")

bind_cols(
  data_s1 |> count(name = "n_study1"),
  data_s2 |> count(name = "n_study2"),
  data_s3 |> count(name = "n_study3")
) |>
  kable() |>
  kable_classic(full_width = FALSE)

```

# n scales

including multi-item self report scales and single item (or small number of items) attitude scales.

```{r}

dat |>
  distinct(scale) |>
  count(name = "n_scales") |>
  kable() |>
  kable_classic(full_width = FALSE)

```

# Range to SD ratio

CIs on M:

$$
m \pm t_{1-\alpha/2, n-1} \left( \frac{s}{\sqrt{n}} \right)
$$

CIs on SD:

$$
\left[ \frac{(n-1)s^2}{\chi^2_{\alpha/2, n-1}}, \frac{(n-1)s^2}{\chi^2_{1-\alpha/2, n-1}} \right]
$$

Three SD-relative metrics computed below: `pomp_sd` = SD / max range (proportion of range, not of max SD); `pomp_sd_popoviciu` = SD / (range/2), the global Popoviciu max-SD bound; `pomp_sd_bd` = SD / sqrt((max - m)(m - min)), the local Bhattacharyya-Davis max-SD bound given the observed mean.


```{r}

# Function to calculate SD CI bounds
# Returns a tibble to allow for easy unnesting if desired, 
# or can be split into two functions.
calc_sd_ci <- function(x, conf_level = 0.95, side = "lower") {
  n <- sum(!is.na(x))
  df <- n - 1
  sd_val <- sd(x, na.rm = TRUE)
  
  alpha <- 1 - conf_level
  
  if (side == "lower") {
    # Chi-square upper critical value for the lower bound
    chi_val <- qchisq(1 - alpha/2, df)
    return(sqrt((df * sd_val^2) / chi_val))
  } else {
    # Chi-square lower critical value for the upper bound
    chi_val <- qchisq(alpha/2, df)
    return(sqrt((df * sd_val^2) / chi_val))
  }
}

dat_nitems <- dat |>
  count(id, scale, subscale) |>
  group_by(scale, subscale) |>
  summarize(n_items = median(n))

calc_pomp <- function(x, min_possible_response, max_possible_response, n_items) {
  ((x - (min_possible_response*n_items)) / ((max_possible_response*n_items) - (min_possible_response*n_items)))
}

# Smithson-Verkuilen transformation
# to offset values from the [0, 1] limits that Beta regression can't handle 
# often used in Beta regression
calc_sk_transf <- function(y, n){
  (y * (n - 1) + 0.5) / n
}


dat_sumscores <- dat |>
  group_by(id, scale, subscale, min_response, max_response) |>
  summarize(sumscore = sum(response, na.rm = TRUE),
            .groups = "drop") |>
  left_join(dat_nitems, by = c("scale", "subscale")) |>
  mutate(pomp_sumscore = calc_pomp(sumscore, 
                                   min_possible_response = min_response, 
                                   max_possible_response = max_response,
                                   n_items = n_items)) |>
  group_by(scale, subscale) |>
  mutate(n = n()) |>
  ungroup() |>
  mutate(pomp_sumscore_sk_transf = calc_sk_transf(pomp_sumscore, n))

# ggplot(dat_sumscores, aes(pomp_sumscore, pomp_sumscore_sk_transf)) +
#   geom_point()

res <- dat_sumscores |>
  group_by(scale, subscale, n_items, min_response, max_response) |>
  summarize(n = n(),
            m = mean(sumscore),
            sd = sd(sumscore),
            # --- Mean CIs (using t-distribution) ---
            # Standard Error: sd / sqrt(n)
            se = sd / sqrt(n),
            # t-critical value for 95% CI
            t_crit = qt(0.975, df = n - 1),
            m_lower = m - (t_crit * se),
            m_upper = m + (t_crit * se),
            sd_lower = calc_sd_ci(sumscore, side = "lower"),
            sd_upper = calc_sd_ci(sumscore, side = "upper"),
            .groups = "drop") |>
  mutate(min_possible = min_response * n_items,
         max_possible = max_response * n_items,
         max_range = max_possible - min_possible,
         # Theoretical max SD bounds:
         # Popoviciu (global): SD <= range / 2, achieved by a 50/50 split at the endpoints.
         # Bhattacharyya-Davis (local, given mean): SD <= sqrt((max - m)(m - min)),
         #   achieved by a two-point distribution at the endpoints with mass set to give mean m.
         max_sd_popoviciu = max_range / 2,
         max_sd_bd        = sqrt((max_possible - m) * (m - min_possible)),
         pomp_m = m/max_range,
         romp_m = max_range/m,
         # Proportion of max range (the original "pomp_sd" — strictly SD/range, not SD/max SD)
         pomp_sd = sd/max_range,
         romp_sd = max_range/sd,
         # Proportion of max SD: global Popoviciu bound, and local Bhattacharyya-Davis bound
         pomp_sd_popoviciu = sd / max_sd_popoviciu,
         pomp_sd_bd        = sd / max_sd_bd) |>
  select(-min_possible, -max_possible, -se, -t_crit) |>
  relocate(sd, .before = sd_lower)

# table
res |>
  mutate_if(is.numeric, roundwork::round_up, digits = 2) |>
  kable() |>
  kable_classic(full_width = FALSE)

temp <- res |>
  mutate_if(is.numeric, roundwork::round_up, digits = 4) |>
  select(scale, subscale, pomp_sd)

```

# POMP distributions

```{r fig.height=16, fig.width=24}

pomp_dist <- dat_sumscores |>
  group_by(scale) |>
  mutate(mean_pomp_sumscore = mean(pomp_sumscore_sk_transf),
         sd_pomp_sumscore = sd(pomp_sumscore_sk_transf)) |>
  ungroup() 

pomp_dist |>
  mutate(scale = fct_reorder(scale, mean_pomp_sumscore)) |>
  ggplot(aes(pomp_sumscore_sk_transf)) +
  geom_rect(aes(xmin = mean_pomp_sumscore - sd_pomp_sumscore, 
                xmax = mean_pomp_sumscore + sd_pomp_sumscore, 
                ymin = -Inf, ymax = Inf), 
            fill = "grey90", alpha = 0.5) +
  geom_vline(aes(xintercept = mean_pomp_sumscore), linetype = 'dashed') +
  geom_density(adjust = 2.5) +
  coord_cartesian(xlim = c(0, 1)) +
  theme_linedraw() +
  facet_wrap(~ scale, scales = "free_y") 

pomp_dist |>
  group_by(scale) |>
  summarize(mean_pomp_sumscore = mean(pomp_sumscore_sk_transf),
            sd_pomp_sumscore = sd(pomp_sumscore_sk_transf)) |>
  mutate_if(is.numeric, round, digits = 3) |>
  arrange(mean_pomp_sumscore) |>
  kable() |>
  kable_classic(full_width = FALSE)

```



```{r fig.height=16, fig.width=24}

# MOM Beta parameters per scale, using the bounds-library function.
# pomp_sumscore_sk_transf is already SK-transformed into (0, 1), so no
# additional offset is needed here. Scales with zero variance (e.g. attention
# checks where everyone gave the same answer) get NA shapes and are dropped
# from downstream Beta plots and bound calculations.
safe_beta_fit_mom <- function(M, SD) {
  if (!is.finite(SD) || SD <= 0 || !is.finite(M) || M <= 0 || M >= 1) {
    return(list(mu = M, sigma_tilde = SD, phi = NA_real_,
                alpha = NA_real_, beta = NA_real_,
                bd_ceiling = NA_real_, impossible = TRUE))
  }
  beta_fit_mom(M, SD, scale_min = 0, scale_max = 1)
}

beta_params <- dat_sumscores |>
  group_by(scale) |>
  summarise(
    m_pomp  = mean(pomp_sumscore_sk_transf, na.rm = TRUE),
    sd_pomp = sd(pomp_sumscore_sk_transf,   na.rm = TRUE),
    .groups = "drop"
  ) |>
  rowwise() |>
  mutate(
    fit = list(safe_beta_fit_mom(m_pomp, sd_pomp)),
    shape1 = fit$alpha,
    shape2 = fit$beta
  ) |>
  ungroup() |>
  select(scale, m_pomp, sd_pomp, shape1, shape2)

# High-res grid for the MOM density curves
grid <- expand_grid(
  scale = unique(dat_sumscores$scale),
  x_val = seq(0.001, 0.999, length.out = 200)
) |>
  left_join(beta_params, by = "scale") |>
  mutate(y_val = dbeta(x_val, shape1, shape2))

# Plot
dat_sumscores |>
  group_by(scale) |>
  mutate(mean_pomp = mean(pomp_sumscore_sk_transf, na.rm = TRUE),
         sd_pomp = sd(pomp_sumscore_sk_transf, na.rm = TRUE)) |>
  ggplot(aes(x = pomp_sumscore_sk_transf)) +
  # Shaded SD region
  geom_rect(aes(xmin = mean_pomp - sd_pomp, xmax = mean_pomp + sd_pomp,
                ymin = -Inf, ymax = Inf), fill = "grey95") +
  # Dashed empirical density for comparison
  geom_density(aes(y = after_stat(density)), adjust = 1, color = "grey60", linetype = "dashed") +
  # MOM Beta density
  geom_line(data = grid, aes(x = x_val, y = y_val), color = "blue", size = 1) +
  geom_vline(aes(xintercept = mean_pomp), linetype = "dashed") +
  theme_linedraw() +
  coord_cartesian(xlim = c(0, 1)) +
  facet_wrap(~ scale, scales = "free_y") +
  labs(x = "POMP sum score", y = "Density",
       caption = "Blue = MOM Beta density. Grey dashed = empirical density.")

```


```{r}

dat_sumscores |>
  group_by(scale) |>
  mutate(mean_pomp = mean(pomp_sumscore_sk_transf, na.rm = TRUE),
         sd_pomp = sd(pomp_sumscore_sk_transf, na.rm = TRUE)) |>
  ggplot(aes(x = pomp_sumscore_sk_transf, color = scale, group = scale)) +
  # MOM Beta densities, one per scale
  geom_line(data = grid, aes(x = x_val, y = y_val), color = "blue", alpha = 0.3, size = 1) +
  theme_linedraw() +
  labs(x = "POMP sum score", y = "Density")

```

# Validating MOM Beta against MLE Beta regression

In production the bound method only has summary statistics (M, SD) to work
from, so the Beta fit must be done by method of moments. To check that
this is a defensible stand-in for a proper-likelihood fit, here we also
fit a constant-precision Beta regression (intercept-only mean, constant
phi) by maximum likelihood on the participant-level data and compare
the recovered (mu, phi) against the MOM estimates.

## Per-scale (mu, phi) from MOM and MLE

```{r}

fit_one_mle <- function(d) {
  tryCatch(
    betareg::betareg(pomp_sumscore_sk_transf ~ 1, data = d),
    error = function(e) NULL
  )
}

mle_fits_list <- split(dat_sumscores, dat_sumscores$scale) |>
  lapply(fit_one_mle)

mle_params <- tibble(
  scale = names(mle_fits_list),
  mu_mle  = vapply(mle_fits_list, function(f) {
    if (is.null(f)) NA_real_ else unname(plogis(coef(f)[["(Intercept)"]]))
  }, numeric(1)),
  phi_mle = vapply(mle_fits_list, function(f) {
    if (is.null(f)) NA_real_ else unname(f$coefficients$precision)
  }, numeric(1))
)

mom_vs_mle <- beta_params |>
  mutate(mu_mom = m_pomp,
         phi_mom = shape1 + shape2) |>
  select(scale, mu_mom, phi_mom) |>
  left_join(mle_params, by = "scale") |>
  mutate(mu_diff   = mu_mle  - mu_mom,
         phi_ratio = phi_mle / phi_mom)

mom_vs_mle |>
  arrange(desc(abs(log(phi_ratio)))) |>
  mutate_if(is.numeric, round, digits = 3) |>
  kable(caption = "Per-scale MOM vs MLE Beta fits, sorted by |log(phi_ratio)|.") |>
  kable_classic(full_width = FALSE)

```

## $\phi_{MOM}$ vs $\phi_{MLE}$ scatter

```{r fig.height=5, fig.width=5}
ggplot(mom_vs_mle, aes(mu_mom, mu_mle)) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "grey50") +
  geom_point(alpha = 0.7) +
  #scale_x_log10() +
  #scale_y_log10() +
  labs(x = "mu (method of moments)",
       y = "mu (Beta regression MLE)",
       caption = "Dashed = MOM matches MLE. Departures flag scales where MOM misleads.") +
  theme_linedraw()

ggplot(mom_vs_mle, aes(phi_mom, phi_mle)) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "grey50") +
  geom_point(alpha = 0.7) +
  scale_x_log10(breaks = breaks_pretty(n = 8)) +
  scale_y_log10(breaks = breaks_pretty(n = 8),
                limits = c(1, 18)) +
  labs(x = "phi (method of moments)",
       y = "phi (Beta regression MLE)",
       caption = "Dashed = MOM matches MLE. Departures flag scales where MOM misleads.") +
  theme_linedraw() +
  theme(panel.grid.minor = element_blank())

ggplot(mom_vs_mle, aes(phi_mom, phi_mle, label = scale)) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "grey50") +
  geom_point(alpha = 0.7) +
  # Add the labels
  geom_text_repel(size = 3, max.overlaps = 15) + 
  scale_x_log10(breaks = breaks_pretty(n = 8)) +
  scale_y_log10(breaks = breaks_pretty(n = 8), limits = c(1, 18)) +
  labs(x = "phi (method of moments)",
       y = "phi (Beta regression MLE)",
       caption = "Dashed = MOM matches MLE. Departures flag scales where MOM misleads.") +
  theme_linedraw() +
  theme(panel.grid.minor = element_blank())
```

The bulk of the scales sit near the diagonal — most multi-item Likert sum scores (BFI factors, Empathy, Self-Compassion, Mindfulness, Grit, Hope, etc.) cluster around phi_ratio ≈ 0.6–0.9. MLE is systematically a bit smaller than MOM (median ratio ≈ 0.78), which is a known small-sample / model-misspecification bias of MOM Beta — it tends to overstate precision when the data has any non-Beta features (mild bimodality, discreteness, mild tails). Order of magnitude is right; the bound you'd compute from MOM would be in the right ballpark.

The interesting failures are all in the upper-left and lower-right of your plot, where mu is near 0 or 1:


```{r}
mom_vs_mle |>
  filter(scale %in% c("pedophile",
                      "fish_legs",
                      "murder",
                      "cats_legs",
                      "racist",
                      "love")) |>
  select(scale, mu_mom, mu_mle, mu_diff, phi_mom, phi_mle, phi_ratio) |>
  mutate_if(is.numeric, round, digits = 3) |>
  kable(caption = "Per-scale MOM vs MLE Beta fits, sorted by |log(phi_ratio)|.") |>
  kable_classic(full_width = FALSE)
```


These are all the single-item attitude items piled up at one end. The mechanism is exactly what the project assumes is the boundary case: when the empirical distribution is mass at a bound + some scatter, the raw variance you feed into MOM is inflated by the clumping, MOM interprets that as low precision, and the SMD bound you'd compute from it would be far too loose — because constant-φ would let SD compress only modestly as the mean shifts, when in reality the post-SD on a piled-up scale shrinks much faster. MLE Beta does better here but neither model is right; the data isn't Beta, it's ZOIB-shaped.

Practical implication for the production method (summary-stats-only):

- For typical bounded sum scores (mu in roughly [0.15, 0.85]), MOM is fine — the plot shows ratio in [0.6, 1.0] for almost all of those scales
- MOM's mild over-estimate of phi means the SMD bound it produces is slightly looser (more permissive) than the MLE bound, which errs on the safe side for plausibility-flagging.
- For scales with mu < 0.15 or mu > 0.85, the MOM bound is unreliable — likely off by a factor of 2–10× in phi, and the constant-φ assumption is broken regardless. 
- The right move in production is a diagnostic flag: warn (or refuse to compute the bound) when the rescaled mean is too close to the bounds (mu < 0.15 or mu > 0.85), because a) no single-Beta model is appropriate there and b) such data is more likely to have weirdly low SDs anyway. Comparisons between two conditions, one of which is running up against the scale bound, will produce very large SMDs that are distorted relative to the unstandardized mean differences.

## Per-scale density: empirical vs MOM Beta vs MLE Beta

```{r fig.height=16, fig.width=24}

mle_grid <- mom_vs_mle |>
  filter(!is.na(phi_mle)) |>
  rowwise() |>
  reframe(
    scale  = scale,
    x_val  = seq(0.001, 0.999, length.out = 200),
    y_val  = dbeta(x_val,
                   shape1 = mu_mle * phi_mle,
                   shape2 = (1 - mu_mle) * phi_mle)
  )

ggplot(dat_sumscores, aes(x = pomp_sumscore_sk_transf)) +
  geom_density(aes(y = after_stat(density)), adjust = 1,
               color = "grey60", linetype = "dashed") +
  geom_line(data = grid,     aes(x = x_val, y = y_val),
            color = "blue",      size = 0.8) +
  geom_line(data = mle_grid, aes(x = x_val, y = y_val),
            color = "firebrick", size = 0.8, linetype = "dotdash") +
  facet_wrap(~ scale, scales = "free_y") +
  coord_cartesian(xlim = c(0, 1)) +
  labs(x = "POMP sum score", y = "Density",
       caption = "Grey dashed = empirical density. Blue solid = MOM Beta. Red dot-dash = MLE Beta.") +
  theme_linedraw()

```

# Per-scale SMD bounds (Beta-implied vs naive)

For each scale, compute the SMD ceilings at the upper and lower scale
endpoints under the naive linear bound (observed SD as denominator) and
the Beta-implied between-groups bound (pooled SD with Beta-predicted
post SD). The pooled bound asymptotes to sqrt(2) x the naive bound at
the endpoints — it is mathematically *looser* than naive there, not
tighter, because it honestly accounts for the fact that observed SD
will compress as the mean approaches a bound. The interesting quantities
are therefore the *absolute* magnitudes of the per-scale ceilings, not
their ratio.

```{r}

safe_smd_bounds <- function(M, SD) {
  if (!is.finite(SD) || SD <= 0 || !is.finite(M) || M <= 0 || M >= 1) {
    return(list(naive  = c(up = NA_real_, down = NA_real_),
                pooled = c(up = NA_real_, down = NA_real_)))
  }
  smd_bounds(M = M, SD = SD, scale_min = 0, scale_max = 1)
}

bounds_per_scale <- beta_params |>
  rowwise() |>
  mutate(
    bounds      = list(safe_smd_bounds(m_pomp, sd_pomp)),
    naive_up    = bounds$naive[["up"]],
    naive_down  = bounds$naive[["down"]],
    pooled_up   = bounds$pooled[["up"]],
    pooled_down = bounds$pooled[["down"]]
  ) |>
  ungroup() |>
  select(scale, m_pomp, sd_pomp,
         naive_up,   pooled_up,
         naive_down, pooled_down)

bounds_per_scale |>
  mutate_if(is.numeric, round, digits = 3) |>
  kable(caption = "Per-scale SMD ceilings at the upper and lower endpoints.") |>
  kable_classic(full_width = FALSE)

```

```{r}

bounds_long <- bounds_per_scale |>
  pivot_longer(cols = c(naive_up, pooled_up, naive_down, pooled_down),
               names_to = "bound_type",
               values_to = "smd") |>
  separate(bound_type, into = c("convention", "direction"), sep = "_") |>
  mutate(direction = recode(direction,
                            up   = "approaching upper bound",
                            down = "approaching lower bound"))

bounds_long |>
  filter(convention == "pooled") |>
  ggplot(aes(smd)) +
  geom_histogram(position = "identity", alpha = 0.5,
                 boundary = 0, binwidth = 0.5) +
  scale_x_continuous(breaks = breaks_pretty(n = 12)) +
  facet_wrap(~ direction, ncol = 1, scales = "free_x") +
  #scale_fill_manual(values = c(naive = "grey40", pooled = "#1a5fb4")) +
  labs(x = "SMD ceiling at endpoint",
       y = "n scales",
       #fill = "denominator",
       caption = "Pooled = Beta-implied between-groups bound. Naive = observed SD as denominator.") +
  theme_linedraw()

bounds_long |>
  filter(convention == "pooled") |>
  ggplot(aes(abs(smd))) +
  geom_histogram(position = "identity", alpha = 0.5,
                 boundary = 0, binwidth = 0.5) +
  scale_x_continuous(breaks = breaks_pretty(n = 12)) +
  #scale_fill_manual(values = c(naive = "grey40", pooled = "#1a5fb4")) +
  labs(x = "Absolute SMD ceiling at either endpoint",
       y = "n scales",
       #fill = "denominator",
       caption = "Pooled = Beta-implied between-groups bound. Naive = observed SD as denominator.") +
  theme_linedraw()

```

- need to split by attitudes, individual differences, and positive controls

# POMP SD & ROMP SD

Three different denominators for "proportion of maximum SD":

- `pomp_sd = sd / max_range` — proportion of max *range* (not really a max-SD bound; kept for back-compat).
- `pomp_sd_popoviciu = sd / (range / 2)` — proportion of the global Popoviciu max SD.
- `pomp_sd_bd = sd / sqrt((max - m)(m - min))` — proportion of the local Bhattacharyya-Davis max SD given the observed mean. Bounded in [0, 1] for any valid (m, sd) on a bounded scale.

```{r}

ggplot(res, aes(pomp_sd)) +
  geom_histogram(boundary = 0, binwidth = .025) +
  scale_x_continuous(name = "SD / max range",
                     breaks = seq(0, 1, by = .1)) +
  scale_y_continuous(name = "Frequency", breaks = seq(0, 100, by = 5)) +
  theme_linedraw()

ggplot(res, aes(pomp_sd_popoviciu)) +
  geom_histogram(boundary = 0, binwidth = .025) +
  scale_x_continuous(name = "SD / Popoviciu max SD (global)",
                     breaks = seq(0, 1, by = .1)) +
  scale_y_continuous(name = "Frequency", breaks = seq(0, 100, by = 5)) +
  theme_linedraw()

ggplot(res, aes(pomp_sd_bd)) +
  geom_histogram(boundary = 0, binwidth = .025) +
  scale_x_continuous(name = "SD / Bhattacharyya-Davis max SD (local, given mean)",
                     breaks = seq(0, 1, by = .1)) +
  scale_y_continuous(name = "Frequency", breaks = seq(0, 100, by = 5)) +
  theme_linedraw()

```

# POMP M

```{r}

ggplot(res, aes(pomp_m)) +
  geom_histogram(boundary = 0, binwidth = .025) +
  scale_x_continuous(name = "POMP M", limits = c(-.05, 1.05), breaks = seq(0, 1, by = .1)) +
  scale_y_continuous(name = "Frequency", breaks = seq(0, 100, by = 1)) +
  theme_linedraw()

```

# 95% CIs on M and SD



```{r}



res <- dat_sumscores |>
  group_by(scale, subscale, n_items) |>
  summarize(n = n(),
            m = mean(sumscore),
            sd = sd(sumscore),
            
            .groups = "drop") |>
  mutate(min_possible = 1 * n_items,
         max_possible = 5 * n_items,
         max_range = max_possible - min_possible,
         pomp_m = m/max_range,
         romp_m = max_range/m,
         pomp_sd = sd/max_range,
         romp_sd = max_range/sd) |>
  select(-min_possible, -max_possible) |>
  relocate(max_range, .before = sd)

```